---
title: "Content & Deliverables"
format: html
editor: visual
---

# Project 1 - Capstone Deliverables

These are deliverables of my MGEM capstone project. The project focus on land cover transition and biomass change in the Mudge and Link study areas using LiDAR and remote sensing data. The study integrates airborne LiDAR metrics, satellite imagery, and forest inventory data to model aboveground biomass and detect land-cover transitions between 2019 and 2024.

By combining machine learning methods with spatial analysis, the project evaluates forest disturbance, regeneration, and stable forest conditions across the landscape. The results provide insights into forest dynamics and demonstrate how remote sensing can support monitoring and management of forest ecosystems.

## Land Cover Transition

The following maps of smoothed land cover classification raster that exhibit land cover distribution over the study area

```{r setup, include=FALSE}
library(terra)
library(leaflet)

```

*2019:*

```{r map2019, echo=FALSE, warning=FALSE, message=FALSE}
rast2019 <- rast("data/classified_2019_smoothed.tif")

# class values and labels
vals2019 <- c(1,2,3,4,5)

labs2019 <- c(
  "Broadleaf Forest",
  "Coniferous Forest",
  "Non-forest vegetation",
  "Water",
  "Others"
)

cols2019 <- c("#A6D96A", "#33A02C", "#F1A026", "#2B83BA", "#DE3B13")

pal2019 <- colorFactor(cols2019, domain = vals2019)

leaflet() %>%
  addProviderTiles("Esri.WorldImagery") %>%
  addRasterImage(rast2019, colors = pal2019) %>%
  addLegend(
    position = "bottomright",
    colors = cols2019,
    labels = labs2019,
    title = "Land-cover classes",
    opacity = 1
  )
```

*2024:*

```{r map2024, echo=FALSE, warning=FALSE, message=FALSE}
rast2024 <- rast("data/classified_2024_smoothed.tif")

# class values and labels
vals2024 <- c(1,2,3,4,5)

labs2024 <- c(
  "Broadleaf Forest",
  "Coniferous Forest",
  "Non-forest vegetation",
  "Water",
  "Others"
)

cols2024 <- c("#A6D96A", "#33A02C", "#F1A026", "#2B83BA", "#DE3B13")

pal2024 <- colorFactor(cols2024, domain = vals2024)

leaflet() %>%
  addProviderTiles("Esri.WorldImagery") %>%
  addRasterImage(rast2024, colors = pal2024) %>%
  addLegend(
    position = "bottomright",
    colors = cols2024,
    labels = labs2024,
    title = "Land-cover classes",
    opacity = 1
  )
```

The transition map shows the transitions types of land cover between 2019 and 2024 over the Mudge Island and the Link Island.

```{r map——transition, echo=FALSE, warning=FALSE, message=FALSE}
rast_trans <- rast("data/transition_3type.tif")

vals_trans <- c(1, 2, 3, 4)

labs_trans <- c(
  "Stable Forest",
  "Regeneration",
  "Disturbance",
  "Others"
)

cols_trans <- c("#2ca02c", "#dce319", "#ff1a1a", "#9e9e9e")

pal_trans <- colorFactor(
  palette = cols_trans,
  domain = vals_trans,
  na.color = "transparent"
)

leaflet() %>%
  addProviderTiles("Esri.WorldImagery") %>%
  addRasterImage(rast_trans, colors = pal_trans) %>%
  addLegend(
    position = "bottomright",
    colors = cols_trans,
    labels = labs_trans,
    title = "Transition type",
    opacity = 1
  )
```

## Code Snippets

Sample code snippet. Notice that you can provide a toggle to switch between coding languages - this is referred to as a 'tabset' in quarto. It is good practice to try and convert your R code to python, and vice-versa to demonstrate coding proficiency. For example, let's showcase a function for calculating NDVI in R and Python.

::: {.panel-tabset group="language"}
## R

``` (.r)
calc_ndvi <- function(nir, red){
  ndvi <- (nir-red)/(nir+red)
  return(ndvi)
}
```

(Assuming *nir* and *red* are terra rast objects)

## Python

``` (.python)
def calc_ndvi(nir, red): 
  ndvi = (nir - red)/(nir + red)
  return(ndvi)
```

(Assuming *nir* and *red* are numpy arrays)
:::

## External links

You can also provide a frame linking to external websites. For example, here is a Google Earth Engine application I developed - which I embedded in this webpage using the code below:

```{code}

<iframe width="900" height="700"
src="https://ee-melserramon.projects.earthengine.app/view/thermal-analysis-tool">
</iframe>
```

The full-screen GEE application is available [here](https://ee-melserramon.projects.earthengine.app/view/thermal-analysis-tool) in case you're interested.

(To use the GEE tool, navigate to any city you'd like, hit apply filters, and click anywhere on the map to retrieve a time-series of Landsat surface temperature observations for that point. Areas where the maximum temp exceeded 35 degrees Celsius in your date-range are highlighted in red.)

```{=html}
<iframe width="900" height="700" src="https://ee-melserramon.projects.earthengine.app/view/thermal-analysis-tool"></iframe>
```
